Sample Length at Which Block Bootstrapping is Effective for Estimation of Parameter of Time Series

### 2023-02-14 Manuscript/manuscript.tex
Small Change

In regular bootstrap procedure, the new pseudo-sample of the same size as the original sample would be created by simply resampling observations from the original sample with replacement. However, in the case of a time series, in order to account for the temporal dependence, the time series can be split into blocks, typically of the same size. The block should be of size $l$ large enough for each pseudo-sample to exhibit some temporal dependence, yet small enough for there to be some variability between each pseudo-sample. Ideally, as $n$ increases, $l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is often assigned a value as a function of $n$. A common function that is considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$. \citep{buhlmann1999block} The designer of the study can choose whether the blocks overlap or not. If the blocks do not overlap, it is called a non-moving block bootstrap. In this case, the original sample is split evenly into blocks, which will then be resampled to create new pseudo-samples. If the blocks do overlap, it is called a moving block bootstrap. Blocks are resampled randomly from the original sample, but they do not have to be from a set of evenly spaced blocks. For moving block bootstrap, if $l \vert n$, a bootstrapped pseudo-sample is created by taking a sample of $n / l$ blocks of size $l$ with replacement to create a new pseudo-sample of size $n$. If $l does not divide n$, the pseudo-sample is created by taking a sample of $\lfloor n / l \rfloor$ blocks of size $l$ and one block of size $(n \;\mathrm{mod})\; l$. An estimate $\hat\theta_n^*$ is computed from the pseudo-sample. This procedure can be repeated many times to create a distribution of $\hat\theta_n^*$.

@@

\[X_{t} = \epsilon_{t} + \phi X_{t-1}.\]
\[Var(X_{t}) = Var(\epsilon_{t} + \phi X_{t-1})\]
\[\sigma^2_{x} = \sigma^2_{\epsilon} + \phi^2 \sigma^2_{x}\]
\[\sigma^2_{x}(1 - \phi^2) = 1\]
\[\sigma_{x}\sqrt{1 - \phi^2} = 1\]

>>>>

In regular bootstrap procedure, the new pseudo-sample of the same size as the original sample would be created by simply resampling observations from the original sample with replacement. However, in the case of a time series, in order to account for the temporal dependence, the time series can be split into blocks, typically of the same size. The block should be of size $l$ large enough for each pseudo-sample to exhibit some temporal dependence, yet small enough for there to be some variability between each pseudo-sample. Ideally, as $n$ increases, $l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is often assigned a value as a function of $n$. A common function that is considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block}. The designer of the study can choose whether the blocks overlap or not. If the blocks do not overlap, it is called a non-moving block bootstrap. In this case, the original sample is split evenly into blocks, which will then be resampled to create new pseudo-samples. If the blocks do overlap, it is called a moving block bootstrap. Blocks are resampled randomly from the original sample, but they do not have to be from a set of evenly spaced blocks. For moving block bootstrap, if $l \vert n$, a bootstrapped pseudo-sample is created by taking a sample of $n / l$ blocks of size $l$ with replacement to create a new pseudo-sample of size $n$. If $l does not divide n$, the pseudo-sample is created by taking a sample of $\lfloor n / l \rfloor$ blocks of size $l$ and one block of size $(n \;\mathrm{mod})\; l$. An estimate $\hat\theta_n^*$ is computed from the pseudo-sample. This procedure can be repeated many times to create a distribution of $\hat\theta_n^*$.

@@

\[X_{t} = \epsilon_{t} + \phi X_{t-1};\]
\[Var(X_{t}) = Var(\epsilon_{t} + \phi X_{t-1});\]
\[\sigma^2_{x} = \sigma^2_{\epsilon} + \phi^2 \sigma^2_{x};\]
\[\sigma^2_{x}(1 - \phi^2) = 1;\]
\[\sigma_{x}\sqrt{1 - \phi^2} = 1.\]
